Binocular combination in the autonomic nervous system

### 2024-06-07 manuscript.Rmd
Removed word limit reminders
Added preprint server information, classification and keywords

@@

# Abstract (250 words)

@@

# Significance statement (120 words)

>>>>

Preprint server: a preprint has been deposited on BioRxiv (https://doi.org/10.1101/2024.06.04.597314) with a no reuse/adaptation without permission license

Classification: Biological Sciences - Psychological and Cognitive Sciences

Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling

@@

# Abstract

@@

# Significance statement

### 2024-06-07 manuscript.tex
Added preprint server information, classification and keywords

\hypertarget{abstract-250-words}{%
\section{Abstract (250 words)}\label{abstract-250-words}}

@@

\hypertarget{significance-statement-120-words}{%
\section{Significance statement (120 words)}\label{significance-statement-120-words}}

The diameter of the pupil depends on the level of ambient light and is controlled by distinct retinal photoreceptor classes (cones, rods and intrinsically photosensitive retinal ganglion cells). The computational processes behind binocular integration within the subcortical pathways controlling pupil dimension have been investigated and have been shown to occur independently of visual cortex. We investigated binocular combination within the different photoreceptor pathways using silent substitution. We found different patterns of binocular combination in each pathway and also differences in the phase of the pupil response. The results are consistent with a computational model of binocular signal combination, where the weight of interocular suppression differs across pathways, and demonstrate the algorithm governing binocular combination in the autonomic nervous system.

>>>>

Preprint server: a preprint has been deposited on BioRxiv (\url{https://doi.org/10.1101/2024.06.04.597314}) with a no reuse/adaptation without permission license

Classification: Biological Sciences - Psychological and Cognitive Sciences

Keywords: Pupil diameter, Pupillometry, Silent substitution, Melanopsin, Binocular combination, Computational modelling

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

@@

\hypertarget{significance-statement}{%
\section{Significance statement}\label{significance-statement}}

Pupil diameters are determined by a network of subcortical nuclei that must combine incoming light levels across the two eyes, independently of cortical visual areas. We investigated the algorithmic properties of this binocular combination process for the first time. Using silent subsitution, we targeted different post-retinal pathways (luminance, L-M cones, S-cones, and melanopsin) with flickering stimuli generated by a novel binocular multi-primary system. We found different patterns of binocular combination across pathways, and also differences in the phase of the pupil response. The results were well described by a computational model of binocular signal combination, in which the weight of suppression between the eyes differed across pathways. This elucidates the algorithm governing binocular combination in the autonomic nervous system.
